Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-05 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Updated transformation of percentage variables

In order to allow for more simplistic and direct interpretations when analyzing the effect of the input variables on the output, it was determined that all percentage variables (senior, poverty, and unemployment) would be transformed into rates per 100,000 to align with the case rate variable. It will also serve to ease the burden on the readers of this report as like-for-like scaled relationships can be drawn between the variables. Given that this transformation is constant for all values (scalar multiplication of 100,000), it will have no effect on the distributions of the variables.

@@

df <-df %>%
  mutate(    
    senior_per_100k = 100000*senior_pct,
    poverty_per_100k = 100000*poverty_pct, 
    unemployed_per_100k = 100000*unemployed_pct,
  )
```

>>>>

In order to allow for more simplistic and direct interpretations when analyzing the effect of the input variables on the output, it was determined that all percentage variables (senior, poverty, and unemployment) would be transformed into rates per 100,000 to align with the case rate variable. It will also serve to ease the burden on the readers of this report as like-for-like scaled relationships can be drawn between the variables. Given that this transformation is constant for all values (scalar multiplication of 100,000 for the seniors variable, and 1,000 for poverty and unemployment), it will have no effect on the distributions of the variables.

@@

df <-df %>%
  mutate(    
    senior_per_100k = 100000*senior_pct,
    poverty_per_100k = 1000*poverty_pct, 
    unemployed_per_100k = 1000*unemployed_pct,
  )
```
